---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ABHgenotypeR
The ABHgenotypeR R package to easily visualize and manipulate ABH genotypes.

## Introduction

The `ABHgenotypeR` package provides simple imputation, error-correction and plotting capacities for genotype data. The function in this package were initially developed for the GBS/QTL analysis pipeline described in:

*Furuta, Reuscher et. al., 2016 Adaption genotyping by sequencing for rice F2
populations. BMC Genomics XYZ*

The `ABHgenotypeR` package is supposed to serve as an intermediate but independent analysis tool between the TASSEL GBS pipeline and the `qtl` package. `ABHgenotypeR` provides functionalities not found in either TASSEL or `qtl` in addition to visualization of genotypes as "graphical genotypes". Plotting is based on ggplot2.


## Installation

from CRAN:
```{r, eval = FALSE}
install.package("ABHgenotypeR")
library(ABHgenotypeR)
```
or from github:

```{r, eval = FALSE}
#needs "devtools"
install.packages("devtools")
library(devtools)

install_github("StefanReuscher/ABHgenotypeR", build_vignettes = TRUE)
```

for more information run:
```{r, eval = FALSE}
vignette("ABHgenotypeR-vignette", package = "ABHgenotypeR")
```
